---
title: "First Blog post"
author: "Catherine Blatter"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(datasauRus)
library(gganimate)
library(gifski)
knitr::opts_chunk$set(echo = FALSE)
```

## Intro

This is my very first blog post and mostly a tryout for using Rmarkdown for Wordpress.
In order to try out numerical code and graphical output, I used the datasaurus-dozen-dataset from the 
[datasauRus-package](https://itsalocke.com/datasaurus/). The awesome thing about these datasets is that while all twelve datasets share the same summary statistics, they look very differently.  
That's where visualization comes around...

Credit to the content of this post goes to [Steph Locke](https://itsalocke.com) and [Mitch O'Hara Wild](https://github.com/numbats/gganimate-workshop/blob/master/index.Rmd) - the gganimate-workshop is a great resource.

### Numerical summary of the datasaurus-dataset

As you can see every dataset shares the same summary statistics...  

```{r sum_num_datsaurus}

datasaurus_dozen %>% 
    group_by(dataset) %>% 
    summarize(
      mean_x    = mean(x),
      mean_y    = mean(y),
      std_dev_x = sd(x),
      std_dev_y = sd(y),
      corr_x_y  = cor(x, y)
    )

```

### Plots

When we visualize this using *ggplot2* we see how different the datasets actually look...  


```{r sum_graph_datasaurus}

ggplot(datasaurus_dozen, aes(x=x, y=y, colour=dataset))+
  geom_point()+
  theme_void()+
  theme(legend.position = "none")+
  facet_wrap(~dataset, ncol=3)

```


### Animation

Last but not least: For the sake of fun we implement code from the [numbats-workshop] (https://github.com/numbats/gganimate-workshop/blob/master/index.Rmd): 

```{r sum_animation_datasaurus}
ggplot(datasaurus_dozen) +
  aes(x, y) +
  geom_point() +
  transition_states(dataset, 3, 1) +
  labs(title = "Dataset: {closest_state}")
```


